Crunching Large Graphs with Commodity Processors

### 2011-01-26 doc/hotpar2011/softxmt-hotpar2011.tex
almost

We presented our plans for building a system for large graph
computation using commodity parts. We leverage decades-old ideas on
using a large amount of concurrency to tolerate latencies; but we do so
mostly in software. We developed a runtime system for latency
tolerance and our results showed that it is able to manage enough
concurrency to tolerate latencies long enough to amortize the cost of
expensive accesses to our large global memory system (high-latency,
but high-bandwidth).

>>>>

We presented our plans for building a system for large graph
computation using commodity parts. We leverage decades-old ideas on
using a large amount of concurrency to tolerate latencies; but we do so
mostly in software. We developed a runtime system for latency
tolerance and our results showed that it is able to manage enough
concurrency to tolerate long latencies to amortize the cost of
expensive accesses to our large global memory system (high-latency,
but high-bandwidth).
